Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-03 main.Rmd
p28 The current version on CRAN is 0.1.3, should that not be used?
p18 Displays are not "equipped with benefits". How about "Each has its own strengths and weaknesses and that should be..."

Plot selection is dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is one that can display distributions using kernel density estimates or descriptive statistics. Displays based on descriptive statistics include variations of box plots [@Tukey1977-jx] such as notched box plots [@Mcgill1978-hg], letter-value plots [@Hofmann2017-sg] or quantile plots. Plots based on kernel density estimates include violin plots [@Hintze1998-zi], summary plot [@Potter2010-qc], ridge line plots, and highest density region (HDR) boxplots [@Hyndman1996-ft]. Each type of density display has parameters that need to be estimated from the data. Each is equipped with some benefits and challenges that should be borne in mind while using them for exploration.

@@

\noindent
**R-package:** The ideas presented in this article have been implemented in the open-source R [@R-language] package `gravitas` [@R-gravitas], available from CRAN. The R-package facilitates manipulation of single and multiple-order-up time granularities through cyclic calendar algebra, checks feasibility of creating plots or drawing inferences for any two cyclic granularities by providing list of harmonies and recommends prospective probability distributions through factors described in the article. Version 0.1.2 of the package was used for the results presented in the article and is available on Github (https://github.com/Sayani07/gravitas).

>>>>

Plot selection is dictated by the statistical transformations and geometric objects used for the visualization. The basic plot choice for our data structure is one that can display distributions using kernel density estimates or descriptive statistics. Displays based on descriptive statistics include variations of box plots [@Tukey1977-jx] such as notched box plots [@Mcgill1978-hg], letter-value plots [@Hofmann2017-sg] or quantile plots. Plots based on kernel density estimates include violin plots [@Hintze1998-zi], summary plot [@Potter2010-qc], ridge line plots, and highest density region (HDR) boxplots [@Hyndman1996-ft]. Each type of density display has parameters that need to be estimated from the data. Each has its own strengths and weaknesses that should be borne in mind while using them for exploration.

@@

\noindent
**R-package:** The ideas presented in this article have been implemented in the open-source R [@R-language] package `gravitas` [@R-gravitas], available from CRAN. The R-package facilitates manipulation of single and multiple-order-up time granularities through cyclic calendar algebra, checks feasibility of creating plots or drawing inferences for any two cyclic granularities by providing list of harmonies and recommends prospective probability distributions through factors described in the article. Version 0.1.3 of the package was used for the results presented in the article and is available on Github (https://github.com/Sayani07/gravitas).
